Behavioural Analysis of Independent Value-Based Learning in Non-cooperative Games

### 2025-06-07 research/paper/paper.tex
data
less key words

\begin{keywords}
Multi-agent; reinforcement learning; independent value-based learning; game theory; non-cooperative games; competitive games; Nash equilibrium; food chain; food web; ecosystem
\end{keywords}

@@

\subsection{Results and Discussion}
We tested the IVBL algorithm IQL and the independent policy-based algorithm IPPO in both scenarios. All experiments ran for 800 iterations. For each iteration, the algorithm collects 640 timesteps as training samples and train the neural network before 50 evaluation games were run. The plots show the average reward for each agent during the evaluation phase. Each experiment was run 20 times to mitigate the effect of randomness and the graphs show the boots trapped 95\% confidence interval. More details of the parameters for the experiments can be found in Table~\ref{table:experiments_parameters} in the appendix.

@@

\section*{Acknowledgements}
The authors sincerely gratitude the creators of the MARL library BenchMARL \cite{bettini2024benchmarl}, which was used to run the experiments.

>>>>

\begin{keywords}
Multi-agent reinforcement learning; independent value-based learning; game theory; non-cooperative games; Nash equilibrium
\end{keywords}

@@

\subsection{Results and Discussion}
We tested the IVBL algorithm IQL and the independent policy-based algorithm IPPO in both scenarios. The experiments were run using the open-source MARL library BenchMARL \cite{bettini2024benchmarl}. All experiments ran for 800 iterations. For each iteration, the algorithm collects 640 timesteps as training samples and train the neural network before 50 evaluation games were run. The plots show the average reward for each agent during the evaluation phase. Each experiment was run 20 times to mitigate the effect of randomness and the graphs show the boots trapped 95\% confidence interval. More details of the parameters for the experiments can be found in Table~\ref{table:experiments_parameters} in the appendix.

@@
